---
title: "Idea present"
subtitle: "😀 😀 😀 <br/> Course project"
author: "Hai vo"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(here)
```



# Idea

  -   Shiny web-app
  
  -   Present BillBoard dataset
  
  -   Use `shinydashboard`, `shinyjs`, `plotly`
  
  -   Source [data](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-09-14/readme.md)
  
---
# The App

1. Link to [App](https://haivo.shinyapps.io/Billboard-performers/)

2. Manual

  -   You just need to choose artist and their song on the sidebar
  
  -   You can click on the the info-box to look at summary data

---


# Main dataset

The main data set contain BillBoard data - top 100s

```{r}
bb = readRDS(here("App/data/billboard.rds"))
bb[c("song", "week_id", "week_position", "performer")] |>
  head(20) |>
  DT::datatable()
```


---
# Addtional dataset 

There are additional data set about the characteristics of song, for example: `energy`, `danceablity`, ` acoustcness`, etc

```{r}
song = readRDS(here("App/data/songs.rds"))
tail(song[,c("song", "energy", "valence", "danceability")], n =5)
```

---

# Thank you!
